---
title: "3MaketBasketAnalysis_DataQuality_JoinTablesandExcludeOutliers"
author: "SuninChoi"
date: "12/5/2019"
output: html_document
Data Quality - Join necessary tables and exclude outliers
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### 1. Read datasets from local computer and load libraries


```{r import dataset, echo=FALSE}
library(tidyverse)
library(ggplot2)
library(funModeling)
library(corrplot)
library(dplyr)
library(ggplot2)
library(readxl)
library(readr)

getwd()
item <- read_csv2("C:/Users/sunny/Desktop/2.R/Function/BrandPreference-MarketBasket/data/line_item.csv")
orders <- read_csv2("C:/Users/sunny/Desktop/2.R/Function/BrandPreference-MarketBasket/data/orders.csv")
products <- read_csv2("C:/Users/sunny/Desktop/2.R/Function/BrandPreference-MarketBasket/data/products.csv")
```



### 2. Basic understanding dataset


```{r basic understanding of dataset, echo=FALSE}
class(item)
dim(item)
head(item)
tail(item)
str(item)
glimpse(item)
summary(item)

```



### 3. Data join and clean
#### 3.1 Create a colume of paid per orders in the line_item table


```{r creating a colume of paid per orders }
item1 <- item %>%  
  mutate(paid_order = unit_price * product_quantity) %>%
  group_by(id_order) %>% 
  summarise(total_paid_order = sum(paid_order))

```



#### 3.2 Join(inner) item and orders tables together
* plus, excluding not"Completed" orders


```{r join item and orders tables}
item1$id_order <- as.character(item1$id_order)
orders$id_order <- as.character(orders$id_order)

item_orders <- item1 %>% 
                 inner_join(orders, by = "id_order")

item_orders <- item_orders %>% 
                na.omit() %>% 
                filter(state == "Completed")

```



#### 3.2.1 Create a column for paid difference between total_paid and paid per orders and exclude outliers by percentage in order to make an adjusted table of item_order


```{r compare total_paid and paid per orders and remove outliers}

itemorders <- item_orders %>% 
  mutate(paiddiffer = total_paid - total_paid_order) 

ggplot(itemorders, aes(total_paid_order, total_paid)) + 
  geom_point() + 
  scale_x_log10() + 
  scale_y_log10()

nrow(itemorders %>% 
       filter(paiddiffer<= 100 & paiddiffer >= -100)) # 46539

# Summarise total paid difference per id_order and the percentage of difference
itemorders1 <- itemorders %>% 
  group_by(id_order) %>% 
  summarise(totalpaiddiffer = sum(paiddiffer), totalpaiddifferperc = paiddiffer/total_paid)

# Exclude outliers and join with line item
fil_it_ord <- itemorders1 %>% 
  filter(totalpaiddifferperc <= 0.3 & totalpaiddifferperc >= -0.3) %>% 
  select(id_order, totalpaiddifferperc)

nrow(fil_it_ord) # 45345

# Join(inner) item and selected order tables
item$id_order <- as.character(item$id_order)
item_filtered_orders <- item %>% 
  inner_join(fil_it_ord, by = "id_order")


```



#### 3.3 Join(inner) item and products tables together and create a colume for price difference between unit_price in item and price in products tables


```{r join item and products tables}
it_pro <- item %>% 
  inner_join(products, by = "sku")

it_pro <- it_pro %>%  
  mutate(pricediffer = price - unit_price, pricedifferperc = unit_price/price)

```



#### 3.3.1 Explore price difference between unit_price and price and the percentage of difference and delete outliers in order to make an adjucted table about item_products
* the minimum price difference is - 159811
* the maximum price difference is 115900091


```{r compare unit_price and price and remove outliers}

it_pro %>%    
    as_tibble() %>% 
      count(pricediffer > 1000) #9028

it_pro %>% 
  as_tibble() %>% 
  count(pricediffer < 0) #5334

nrow(it_pro %>% filter(pricediffer > 100)) #42020
nrow(it_pro %>% filter(pricediffer < -100)) #1693

# Outliers by percentage and exclude 30% of them
it_pro <- it_pro %>%  
  mutate(pricediffer = price - unit_price, pricedifferperc = unit_price/price)

fil_it_pro <- it_pro %>% 
  filter(pricedifferperc <= 0.3 & pricedifferperc >= -0.3)

nrow(fil_it_pro) #12176

# Join(inner) item and selected product tables
item$id_order <- as.character(item$id_order)
item_filtered_products <- 
  item %>% inner_join(fil_it_pro, by = "id_order")

```



#### 3.4 Join item, orders, products tables and create a table for a transaction file


```{r join tables and create a table for a transaction file}

# Join three tables
filtered_rev_iop <- item_filtered_orders %>% 
  inner_join(item_filtered_products, by = "id_order")

filtered_rev_iop <- filtered_rev_iop %>% 
  select(id_order, sku.x)

trsfile <- filtered_rev_iop %>% 
  left_join(products, by = c("sku.x" = "sku"))

# Create transactional files with name_en, brand and categories
trsfile <- trsfile %>% 
  na.omit() %>% 
  select(id_order, sku.x, name_en, brand, manual_categories)

trsfile_name <- trsfile %>% 
  na.omit(name_en) %>% 
  select(id_order, name_en)

trsfile_brand <- trsfile %>% 
  na.omit(brand) %>% 
  select(id_order, brand)

trsfile_cate <- trsfile %>% 
  na.omit(manual_categories) %>% 
  select(id_order, manual_categories)

# Because of multiple times joins, redundant sku show so i can choose just one of them because it included in one sku already. 
```



### 4. Export the last table as an excel file


```{r id_order and sku}
library(writexl)

# id_order with product name
write.table(trsfile_name, "trsfile_name.txt", col.names = T, row.names = T, sep = "Wt")
write.csv(trsfile_name, "trsfile_name.csv", row.names = T)
write_xlsx(trsfile_name, path = "C:/Users/sunny/Desktop/2.R/Function/BrandPreference-MarketBasket/data/trsfile_name.xlsx", col_names = TRUE)

# id_order with brands
write.table(trsfile_brand, "trsfile_brand.txt", col.names = T, row.names = T, sep = "Wt")
write.csv(trsfile_brand, "trsfile_brand.csv", row.names = T)
write_xlsx(trsfile_brand, path = "C:/Users/sunny/Desktop/2.R/Function/BrandPreference-MarketBasket/data/trsfile_brand.xlsx", col_names = TRUE)

# id_order with categories
write.table(trsfile_cate, "trsfile_cate.txt", col.names = T, row.names = T, sep = "Wt")
write.csv(trsfile_cate, "trsfile_cate.csv", row.names = T)
write_xlsx(trsfile_cate, path = "C:/Users/sunny/Desktop/2.R/Function/BrandPreference-MarketBasket/data/trsfile_cate.xlsx", col_names = TRUE)

```
