---
title: "4MarketBasketAnalysis_Apriori_CreateTransactionalFiles"
author: "SuninChoi"
date: "12/5/2019"
output: html_document
Arules package and apriori algorithm to create transactional files for recommendation systems
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Market Basket Analysis
## Arules package and apriori algorithm

### 1. Load trasaction dataset (id_order - name, id_order - brand, id_order - categories)


```{r cars}
library(arules)
library(arulesViz)
library(tidyverse)
library(ggplot2)
library(funModeling)
library(corrplot)
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(readxl)
library(readr)

trs_name <- read_csv2("C:/Users/sunny/Desktop/2.R/Function/BrandPreference-MarketBasket/data/trsfile_name.csv")

trs_brand <- read_csv2("C:/Users/sunny/Desktop/2.R/Function/BrandPreference-MarketBasket/data/trsfile_brand.csv")

trs_cate <- read_csv2("C:/Users/sunny/Desktop/2.R/Function/BrandPreference-MarketBasket/data/trsfile_cate.csv")

Lt_name <- read.transactions(
        file = "C:/Users/sunny/Desktop/2.R/Function/BrandPreference-MarketBasket/data/trsfile_name.csv",
        format = "single",
        header = TRUE,
        sep = ",",
        cols = c("id_order","name_en"),
        rm.duplicates = T)

Lt_brand <- read.transactions(
        file = "C:/Users/sunny/Desktop/2.R/Function/BrandPreference-MarketBasket/data/trsfile_brand.csv",
        format = "single",
        header = TRUE,
        sep = ",",
        cols = c("id_order","brand"),
        rm.duplicates = T)

Lt_cate <- read.transactions(
        file = "C:/Users/sunny/Desktop/2.R/Function/BrandPreference-MarketBasket/data/trsfile_cate.csv",
        format = "single",
        header = TRUE,
        sep = ",",
        cols = c("id_order","manual_categories"),
        rm.duplicates = T)
```


### 2. Get to know basic item sets and association rules
#### 2.1 id_order and product names
##### 2.1.1 Exploring dataset
* What are the most frequent items? 
+ 1st. Crucial memory Mac 16GB (2x8GB) SO-DIMM DDR3 1600MHZ: 168
+ 2nd. Rugged Messenger Zagg iPad Keyboard Folio (2017) 97 Backlit Black: 161
+ 3rd. Apple iPhone 64GB X Silver: 130
+ 4th. Zagg Folio Case Color Keyboard Folio iPad Air 2 Black: 120
+ 5th. Jawbone UP2 Black Rope Activity Monitor: 93
+ Other 3531

* How many items do customers purchase the most? Least? 
+ sizes
+    1    2    3    4    5    6    7    8    9   10   11 
+ 1371  542  276  113   45   22    5    2    1    4    1 

* What's the average? 
+ Min.  1st Qu.  Median    Mean 3rd Qu.    Max. 
+ 1.000   1.000   1.000   1.764   2.000  11.000 


```{r exploring transactional dataset of id_order and product names}

# Exploring transactional dataset between id_order and product names
summary(Lt_name)
inspect(Lt_name[1:10]) # view the transactions
length(Lt_name) # number of transaction 2382
size(Lt_name) # number of items per transaction
list(Lt_name) #2382 transactions and 1186 items
LIST(Lt_name) # lists the transactions by conversation
itemLabels(Lt_name) # see the item labels
```


##### 2.1.2 Visualizing dataset with itemFrequencyPlot


```{r utilizing itemFrequencyPlot}
# Visualizing association rules with itemFrequencyPlot
image(Lt_name, method = "graph",  engine = "htmlwidget")

image(sample(Lt_name, 100))

```



##### 2.1.3 Applying apriori algorithm for market basket analysis 
* Create association rules related to product names
+ support: 0.0015, confidence: 0.05
+ 1186 item(s), 2382 transaction(s), 83 rule(s)


```{r}
# Applying apriori algorithm for market basket analysis
rule_name <- apriori(Lt_name, parameter = list(supp=0.0015, conf=0.05, minlen=2, maxlen=8, smax=1))

summary(rule_name)

inspect(rule_name[1:10])

plot(rule_name, method = "graph",  engine = "htmlwidget")

# Exploring various plots
plot(rule_name, control = list(col=brewer.pal(11,"Spectral")))
plot(rule_name, method="two-key plot")
plot(rule_name, method = "grouped")
plot(rule_name, method = "graph")
plot(rule_name[1:10], method = "graph", control = list(type = "items"))
plot(rule_name, method = "matrix", measure = "lift", control = list(col=brewer.pal(11, "Spectral")))
plot(rule_name, method = "matrix3D", measure = "lift")
plot(rule_name, method = "paracoord", control = list(reorder = TRUE))


```


* Diverse ways of filtering association rules based on confidence, life, support


```{r various filtering ways of association rules}
# Create subset of association rules based on high confidence
subrule_name<- rule_name[quality(rule_name)$confidence>0.4]
plot(subrule_name)
plotly_arules(subrule_name)

# Filter top 10 rules with highest confidence 
top10subrule_name <- head(subrule_name, n = 10, by = "confidence")
plot(top10subrule_name, method = "graph",  engine = "htmlwidget")
saveAsGraph(head(subrule_name, n = 1000, by = "lift"), file = "rules.graphml")

# Filter top 20 rules with highest lift
subrule_name2<-head(subrule_name, n=20, by="lift")
plot(subrule_name2, method="paracoord")

subrule_name3 <-sort(subrule_name, by="confidence",decreasing = TRUE)
inspect(subrule_name3[1:5])

```



#### 2.2 id_order and brands
##### 2.2.1 Exploring dataset
2382 rows 115 columns

* What are the most frequent items?
+ 1st. Apple - 599
+ 2nd. ZaggKeys - 340  
+ 3rd. Pack - 290
+ 4th. Crucial - 269
+ 5th. Jawbone - 153
+ Other - 2094 

* How many items do customers purchase the most? Least? (source for Loyal customers, related brands)
+   1    2    3    4    5    6    7    8    9 
+1508  539  222   84   23    3    1    1    1 

* What's the average? 
+   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
+ 1.000   1.000   1.000   1.572   2.000   9.000 


```{r exploring transactional dataset of id_order and brands}
summary(Lt_brand)
inspect(Lt_brand[1:10]) # view the transactions
length(Lt_brand) # number of transaction
size(Lt_brand[1:10]) # number of items per transaction
list(Lt_brand)
LIST(Lt_brand) # lists the transactions by conversation
itemLabels(Lt_brand) # see the item labels

```


##### 2.2.2 Visualizing dataset with itemFrequencyPlot
* the first brand(Apple) is almost double size of 2nd brand(ZaggKeys)


```{r visualizing dataset with itemFrequencyPlot}

itemFrequencyPlot(Lt_brand, topN=10, type="absolute", col=brewer.pal(8,'Pastel2'), main="Absolute Item Frequency Plot")

itemFrequencyPlot(Lt_brand, topN=10, type="relative", col=brewer.pal(8,'Pastel2'), main="Relative Item Frequency Plot")
image(sample(Lt_brand, 100))
```


##### 2.2.3 Applying apriori algorithm for market basket analysis 
* Create association rules related to brands
+ support: 0.004, confidence: 0.06
+ 115 item(s), 2382 transaction(s), 53 rule(s)


```{r apriori algorithm and plots for market basket analysis based on brands}
# Applying apriori algorithm for market basket analysis
rule_brand <- apriori(Lt_brand, parameter = list(supp=0.004, conf=0.06, minlen=2, maxlen=8, smax=1))

summary(rule_brand)

inspect(rule_brand[1:10])

plot(rule_brand, method = "graph",  engine = "htmlwidget")
plot(rule_brand[1:20], method = "graph", control = list(type = "items"))

# Exploring various plots
plot(rule_brand, control = list(col=brewer.pal(11,"Spectral")))
plot(rule_brand, method="two-key plot")
plot(rule_brand, method = "grouped")
plot(rule_brand, method = "graph")
plot(rule_brand, interactive = TRUE)
plot(rule_brand, method = "matrix", measure = "lift", control = list(col=brewer.pal(11, "Spectral")))
plot(rule_brand, method = "matrix3D", measure = "lift")
plot(rule_brand, method = "paracoord", control = list(reorder = TRUE))

```



#### 2.3 id_order and categories
##### 2.3.1 Exploring dataset
2382 rows and 12 columns (categories)

* What are the most frequent items?
+ accessories  smartphone     display     service       other     (Other) 
+        1900         298         168         133         109         186 

* How many items do customers purchase the most? Least? 
+    1    2    3    4    5 
+ 2037  285   54    5    1 
+ Most of times, customers buy just one category product up to 5 categories

* What's the average? 
+   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
+ 1.000   1.000   1.000   1.173   1.000   5.000 


```{r}
summary(Lt_cate)
inspect(Lt_cate) # view the transactions
length(Lt_cate) # number of transaction
size(Lt_cate) # number of items per transaction
list(Lt_cate)
LIST(Lt_cate) # lists the transactions by conversation
itemLabels(Lt_cate) # see the item labels
```


##### 2.3.2 Visualizing dataset with itemFrequencyPlot
* Transaction quatity of accessories dominate that of every other categories


```{r}
itemFrequencyPlot(Lt_cate, topN=10, type="absolute", col=brewer.pal(8,'Pastel2'), main="Absolute Item Frequency Plot")

itemFrequencyPlot(Lt_cate, topN=10, type="relative", col=brewer.pal(8,'Pastel2'), main="Relative Item Frequency Plot")

image(sample(Lt_cate, 100))

```


##### 2.3.3 Applying apriori algorithm for market basket analysis 
* Create association rules related to categories
+ support: 0.001, confidence: 0.02
+ 12 item(s), 2382 transaction(s), 51 rule(s)


```{r apriori algorithm and plots for market basket analysis based on categories}
# Applying apriori algorithm for market basket analysis
rule_cate <- apriori(Lt_cate, parameter = list(supp=0.001, conf=0.02, minlen=2, maxlen=8, smax=1))

summary(rule_cate)

inspect(rule_cate[1:10])

plot(rule_cate, method = "graph",  engine = "htmlwidget")
plot(rule_cate[1:20], method = "graph", control = list(type = "items"))

# Exploring various plots
plot(rule_cate, control = list(col=brewer.pal(11,"Spectral")))
plot(rule_cate, method="two-key plot")
plot(rule_cate, method = "grouped")
plot(rule_cate, method = "graph")
plot(rule_cate, interactive = TRUE)
plot(rule_cate, method = "matrix", measure = "lift", control = list(col=brewer.pal(11, "Spectral")))
plot(rule_cate, method = "matrix3D", measure = "lift")
plot(rule_cate, method = "paracoord", control = list(reorder = TRUE))

```

